H52F-05H: Robust Adaptation to\\Multi-Scale Climate Variability

### 2018-12-04 slides-agu/presentation.tex
add a shameless plug

\begin{frame}{Some Potential Implications}
  \begin{table}
    \begin{tabular}{L{0.425\textwidth}L{0.525\textwidth}}
      \toprule
      Question & Analysis \\\midrule
      Linear trend models? & No, that was just for demonstration -- avoid un-physical extrapolation \\\midrule
      Use only last 30 years to address nonstationarity? & No, this increases variance; use paleo records, observations, and climate models for risk estimation \\\midrule
      Build large infrastructure to manage a changing climate? & Sometimes, but consider alternatives, including postponing construction to increase $N$\\
      \bottomrule
    \end{tabular}
  \end{table}
\end{frame}

>>>>

\begin{frame}{A Shameless Pitch!}
  I'm working to quantify these principles.
  Specifically:
  \begin{itemize}
    \item Statistical models for integrating paleo records, observations, and GCMs towards climate risk projection
    \item Financial valuation of the ``option'' to build a particular project
    \item Optimizing portfolios of long- and short-term investments
  \end{itemize}
  If you have a working model of your system and are making long-/short-term investment choices I'd \alert{love to talk} further!
\end{frame}
